Optimal (Multiway) Spatial Joins

### 2024-05-22 msj.tex
yufei

>>>>

Let us now focus on any $k$-tuple $(r_1, ..., r_{k-2}, h, v) \in  \J_k(R_1, ..., R_{k-2},$ $H, V)$. We classify the tuple into one of the two categories below:

\myitems{
    \item {{\bf Cat.\ 1:}} $h$ crosses all of $r_1, ..., r_{k-2}$, and $v$  crosses all of $r_1, ..., r_{k-2}$;

    \item {{\bf Cat.\ 2:}} $h$ or $v$ fails to cross some rectangle in $\set{r_1, r_2, ..., r_{k-2}}$. 
}
